Tampering Detection In Low-Power \\ Smart Cameras

### 2015-06-22 paper.tex
Cambiati assi ROC

\section{Introduction}\label{sec:introduction}
% What is the problem?
Cameras operating outdoor and in harsh environments are exposed to atmospheric phenomena and intentional attacks that might prevent the correct image acquisition. Rain, snow, dust lying on the camera lens cause blurry (Figure \ref{fig:pioggia}) or partially occluded (Figure \ref{fig:neve}) pictures, while wind might displace the camera (Figure \ref{fig:displ1} -\ref{fig:displ2}). Similarly, an attacker can intentionally change the camera focus, spray some opaque or glossy liquid, displace or occlude the camera. We refer to these events/attacks as tampering. In many situations, tampering is not straightforward to detect (e.g. when the camera is not physically damaged and does not go out-of-order), and image analysis techniques are the only viable option.

@@

% Why is it interesting and important?
Tampering detection is an essential feature in surveillance systems~\cite{hampapur2005smart}, which are expected to autonomously detect any tampering, and promptly report alerts. Tampering, in fact, might result in images that are useless for monitoring purposes: even a mild blur might hinder the identification of important details such as licence plates. Surveillance cameras most often operate at normal frame-rates (e.g. around few frames per second) and are connected to the power supply. Tampering-detection for surveillance cameras have been quite investigated in the literature; in particular, camera displacements and occlusions are typically detected by comparing the current frame against an estimate of the scene background, while blurring is detected by monitoring the high-frequency components of images, as these are expected to drop. In~\cite{aksay2007camera} and~\cite{saglam2009real} tampering is detected by comparing the histograms of background and current frame, and by monitoring the energy in wavelet or Fourier domain. Two background models, estimated over different time intervals, are used in~\cite{saglam2009real}. In~\cite{gil2007automatic}, tampering detection is performed by combining background subtraction together with edge detection and normalized cross-correlation. Background estimates and block matching in~\cite{tsesmelis2013tamper} enable the displacement detection, while the number of SURF~\cite{bay2006surf} keypoints is used to detect blurring. A buffer of recent frames rather than an explicit background is used~\cite{ribnick2006real}. All the above solutions, including~\cite{harasse2004automated,kryjak2012fpga} are computationally demanding, and are not viable options for low-power cameras.

>>>>

\section{Introduction}\label{sec:introduction}
% What is the problem?
Cameras operating outdoor and in harsh environments are exposed to atmospheric phenomena and intentional attacks that might prevent the correct image acquisition. Rain, snow, dust lying on the camera lens cause blurry (Figure \ref{fig:pioggia}) or partially occluded (Figure \ref{fig:neve}) pictures, while wind might displace the camera (Figure \ref{fig:displ1} - \ref{fig:displ2}). Similarly, an attacker can intentionally change the camera focus, spray some opaque or glossy liquid, displace or occlude the camera. We refer to these events/attacks as tampering. In many situations, tampering is not straightforward to detect (e.g. when the camera is not physically damaged and does not go out-of-order), and image analysis techniques are the only viable option.

@@

% Why is it interesting and important?
Tampering detection is an essential feature in surveillance systems~\cite{hampapur2005smart}, which are expected to autonomously detect any tampering, and promptly report alerts. Tampering, in fact, might result in images that are useless for monitoring purposes: even a mild blur might hinder the identification of important details such as licence plates. Surveillance cameras most often operate at normal frame-rates (e.g. around few frames per second) and are connected to the power supply. Tampering detection for surveillance cameras have been quite investigated in the literature; in particular, camera displacements and occlusions are typically detected by comparing the current frame against an estimate of the scene background, while blurring is detected by monitoring the high-frequency components of images, as these are expected to drop. In~\cite{aksay2007camera} and~\cite{saglam2009real} tampering is detected by comparing the histograms of background and current frame, and by monitoring the energy in wavelet or Fourier domain. Two background models, estimated over different time intervals, are used in~\cite{saglam2009real}. In~\cite{gil2007automatic}, tampering detection is performed by combining background subtraction together with edge detection and normalized cross-correlation. Background estimates and block matching in~\cite{tsesmelis2013tamper} enable the displacement detection, while the number of SURF~\cite{bay2006surf} keypoints is used to detect blurring. A buffer of recent frames rather than an explicit background is used~\cite{ribnick2006real}. All the above solutions, including~\cite{harasse2004automated,kryjak2012fpga} are computationally demanding, and are not viable options for low-power cameras.
